Constraint Programming - Inside Gecode

### 2014-05-08 paper.tex
extended introduction

	In the following I will describe the necessary steps to solve a problem with constraint programming and as example of an implementation I will always refer to \emph{Gecode} \cite{gecode}.

>>>>

	In the following I will describe the necessary steps to describe and solve a problem with constraint programming: Variables, constraints, search trees, constraint propagation and search algorithms. As example of an implementation I will always refer to \emph{Gecode} \cite{gecode}.
